### 2018-06-11 Shiva Dissertation/chap/abs.tex
Still requires some edits.

Microrobotics has the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  The same properties that promise breakthrough solutions---small size and large populations---present unique challenges for controlling motion. 
Robotic manipulation usually assumes intelligent agents, not particle systems manipulated by a global signal.
 Adding additional particles to steer makes the system underactuated because there are more states than control inputs. 
 Rather than focusing on a specific microrobotic system, this dissertation designs control laws and algorithms for steering many particles controlled by global fields.

@@

 Second, this dissertation proves that swarm torque control is possible, then presents algorithms to automate the task. 
 Magnetic actuation has the benefits of requiring no tethers, being able to operate from a distance, and in some cases allows imaging for feedback (e.g. MRI).

>>>>

Microrobotics has the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  The same properties that promise breakthrough solutions---small size and large populations---present unique challenges for controlling motion. 
%Robotic manipulation usually assumes intelligent agents, but particle systems manipulated by a global signal.
 When there are more particles than control inputs the system is underactuated and requires new control techniques.
 Rather than focusing on a specific microrobotic system, this dissertation designs control laws and algorithms for steering many particles controlled by global fields.

@@

 Second, this dissertation proves that swarm torque control is possible, then presents algorithms to automate the task. Torque control enables us to control the position and orientation of an object.
% Magnetic actuation has the benefits of requiring no tethers, being able to operate from a distance, and in some cases allows imaging for feedback (e.g. MRI).

### 2018-06-11 Shiva Dissertation/chap/conclusion.tex
Still requires some edits.

 \section{Future Work}
 This dissertation provides foundational algorithms and techniques for steering swarms, object manipulation, and addressing obstacle fields, but there are many opportunities to extend the work.
 Our future goal is to perform assembly using particle swarms to manipulate and attach components. Future efforts should be directed toward examining the effects of Brownian noise, pose control for multiple-part assembly, trajectory prediction, and manipulation in crowded workspaces.
 We assumed friction was sufficient to completely stop particles in contact with the boundary. 
  The algorithms would require retooling to handle small friction coefficients.

>>>>

 \section{Future work}

 Today there are more robots than ever before.
 This dissertation provides foundational algorithms and techniques for steering swarms, object manipulation, and addressing obstacle fields, but there are many opportunities to extend the work.
 Our future goal is to perform assembly using particle swarms to manipulate and attach components. Future efforts should be directed toward examining the effects of Brownian noise, pose control for multiple-part assembly, trajectory prediction, and manipulation in crowded workspaces.
 We assumed friction was sufficient to completely stop particles in contact with the boundary. 
  The algorithms would require retooling to handle small friction coefficients.

### 2018-06-11 Shiva Dissertation/chap/intro.tex
Still requires some edits.

\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =0.2\figwid]{first.png}\put(3,97){a)}
\end{overpic}
\begin{overpic}[width =0.2\figwid]{second.png}\put(3,95){b)}
\end{overpic}
\begin{overpic}[width =0.25\figwid]{third.png}\put(3,85){c)}
\end{overpic}
\begin{overpic}[width =0.25\figwid]{fourth.png}\put(3,85){d)}
\end{overpic}
\caption{\label{fig:model} %Controlling a swarm of robots with global inputs. 
a) The robots are actually simple particles that can be controlled by a global force. b) All the particles get the same control input. c,d) Breaking the symmetry is only possible with external boundary or obstacle.
}
\end{figure}
\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{MicroRobotics.png}
\end{overpic}
\caption{\label{fig:microrobotics} %Controlling a swarm of robots with global inputs. 
Microrobots has the potential to revolutionize medical applications. Figure courtesy:  \cite{nelson2010microrobots}.
}
\end{figure}

Large populations of micro- and nanorobots are being produced in laboratories around the world, with diverse potential applications in drug delivery and construction, see \cite{Peyer2013,Shirai2005,Chiang2011}. These activities require robots that behave intelligently.
Our vision is for large swarms of robots to be remotely guided 1) through the human body, to cure disease, heal tissue, and prevent infection and 2) ex vivo to assemble structures in parallel \cite{nelson2010microrobots}. 
 For each application, large numbers of micro robots are required  to deliver sufficient payloads.
 Often particles are difficult or impossible to sense individually due to their size and location. 
For example, microrobots are smaller than the minimum resolution of a clinical MRI-scanner, see \cite{martel2014computer}, however it is often possible to sense global properties of the group such as mean position and variance. 
 Limited computation and communication at small scales also makes autonomous operation or direct control over individual robots difficult. 
  Instead, this dissertation treats the robots that are steered by a global control signal broadcast to the entire population. 
  The tiny robots themselves are often just rigid bodies, and it may be more accurate to define the robot as the \emph{system} that consists of particles, a uniform control field, and sensing.
 Particle swarms propelled by a uniform field, where each particle  receives the same control input, are common in applied mathematics, biology, and computer graphics \cite{Peyer2013,Shirai2005,Chiang2011}. 
% The transportation methodology is similar to that in~\cite{sugawara2014object}, but rather than using onboard computation or sensing, the particles all move in the same direction.
Such systems are severely underactuated, having 2 degrees of freedom in the shared planar control input, but $2n$ degrees of freedom for the $n$-particle swarm. Figure \ref{fig:model} shows an example of simple particles when they all get the same control input.
 Techniques are needed that can handle this underactuation.

@@

\begin{overpic}[width=0.45\columnwidth]{firstpicLeft.pdf}\put(28,-10){workspace}\end{overpic}
\begin{overpic}[width=0.45\columnwidth]{magneticsetup.pdf}\put(22,-8){magnetic setup}\end{overpic}
\vspace{3em}
\caption{\label{fig:chapters} 
Top left: Chapter 2 discusses steering a swarm of particles using global inputs and swarm statistics. Top right: Chapter 3 goes deep into the torque control of the swarm and orientation control of the object. Bottom Chapter 4 demonstrates algorithms to control position of two robots in any convex workspace when the walls have non-slip contact. %Bottom right: the magnetic setup that is used to manipulate magnetic particles when they both get the same control input.
}
\end{figure}

>>>>

\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{MicroRobotics.png}
\end{overpic}
\caption{\label{fig:microrobotics} %Controlling a swarm of robots with global inputs. 
Microrobots has the potential to revolutionize medical applications. Used with permission from \cite{nelson2010microrobots}.
}
\end{figure}
\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =0.2\figwid]{first.png}\put(3,97){a)}
\end{overpic}
\begin{overpic}[width =0.2\figwid]{second.png}\put(3,95){b)}
\end{overpic}
\begin{overpic}[width =0.25\figwid]{third.png}\put(3,85){c)}
\end{overpic}
\begin{overpic}[width =0.25\figwid]{fourth.png}\put(3,85){d)}
\end{overpic}
\caption{\label{fig:model} %Controlling a swarm of robots with global inputs. 
a) The robots are actually simple particles that can be controlled by a global force. b) All the particles get the same control input. c,d) Breaking the symmetry is only possible with external boundary or obstacle.
}
\end{figure}
Large populations of micro- and nanorobots are being produced in laboratories around the world, with diverse potential applications in drug delivery and construction, see \cite{Peyer2013,Shirai2005,Chiang2011}. These activities require robots that behave intelligently.
Our vision is for large swarms of robots to be remotely guided 1) through the human body, to cure disease, heal tissue, and prevent infection shown in Fig. \ref{fig:microrobotics} \cite{nelson2010microrobots} and 2) ex vivo to assemble structures in parallel. 
 For each application, large numbers of micro robots are required  to deliver sufficient payloads.
 Often particles are difficult or impossible to sense individually due to their size and location. 
For example, microrobots are smaller than the minimum resolution of a clinical MRI-scanner, see \cite{martel2014computer}, however it is often possible to sense global properties of the group such as mean position and variance. 
 Limited computation and communication at small scales also makes autonomous operation or direct control over individual robots difficult. 
  Instead, this dissertation treats the robots that are steered by a global control signal broadcast to the entire population. 
  The tiny robots themselves are often just rigid bodies, and it may be more accurate to define the robot as the \emph{system} that consists of particles, a uniform control field, and sensing.
 Particle swarms propelled by a uniform field, where each particle  receives the same control input, are common in applied mathematics, biology, and computer graphics \cite{Peyer2013,Shirai2005,Chiang2011}. 
% The transportation methodology is similar to that in~\cite{sugawara2014object}, but rather than using onboard computation or sensing, the particles all move in the same direction.
Such systems are severely underactuated, having 2 degrees of freedom in the shared planar control input, but $2n$ degrees of freedom for the $n$-particle swarm. Figure \ref{fig:model} shows an example of simple particles when they all get the same control input.
 Techniques are needed that can handle this underactuation.

@@

\begin{overpic}[width=0.45\columnwidth]{firstpicLeft.pdf}\put(28,-10){workspace}\end{overpic}
\begin{overpic}[width=0.45\columnwidth]{magneticsetup.pdf}\put(22,-8){magnetic setup}\end{overpic}
\vspace{3em}
\caption{\label{fig:chapters} 
Top left: Chapter 2 discusses steering a swarm of particles using global inputs and swarm statistics. Top right: Chapter 3 goes deep into the torque control. Bottom: Chapter 4 demonstrates algorithms to position two robots. %Bottom right: the magnetic setup that is used to manipulate magnetic particles when they both get the same control input.
}
\end{figure}
